Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add a comment

\begin{quote}
BDD tools should be treat both of them and provide functionality
to extract evidence for users as user documentation.
If we can archive this, BDD tools can be used for
triple purpose: design, documentation and automatic testing.
\end{quote}

@@

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.
If the equations above are examples, we cannot distinguish
their results from their expression to be evaluated.
If they are properties, they should be distinguished
from example code.

>>>>

\begin{quote}
    sol: remove?

BDD tools should be treat both of them and provide functionality
to extract evidence for users as user documentation.
If we can archive this, BDD tools can be used for
triple purpose: design, documentation and automatic testing.
\end{quote}

@@

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.

\begin{quote}
    \emph{sol: I think the comment contains properties.  So the
    argumentation makes not really sense?}
\end{quote}

If the equations above are examples, we cannot distinguish
their results from their expression to be evaluated.
If they are properties, they should be distinguished
from example code.
